### 2014-07-01 Quality_Reports/PCR_bottleneck.Rmd
Fixed figure 2 and added observations

```{r boxplot_strand,include = TRUE,echo = FALSE,results = "hide",fig.height = 4}
tab1 = lapply(tab[3:1],function(x)rbind(data.frame(type = x$type,PBC = x$PBC_plus,strand = "+"),
  data.frame(type = x$type,PBC = x$PBC_minus,strand = "-")))
df1 = do.call(rbind,tab1)
df1$type = factor(df1$type)
df1$strand = factor(df1$strand)
p1 <- ggplot(df1,aes(strand,PBC))+geom_boxplot()+facet_grid(.~type)+
  theme(legend.position = "none")
print(p1)
```

- For this plot, the PBC coefficents was calculated using only the reads with certain strand. In particular, we can see that for all 3 types, the boxplots for both strands are very similar.
- The observations of figure 1 hold for both strands.

>>>>

```{r boxplot_strand,include = TRUE,echo = FALSE,results = "hide",fig.height = 4}
tab1 = lapply(tab[3:1],function(x)rbind(data.frame(type = x$type,PBC = x$PBC_plus,strand = "+"),
  data.frame(type = x$type,PBC = x$PBC_minus,strand = "-"),data.frame(type = x$type, PBC = x$PBC,strand = "both")))
df1 = do.call(rbind,tab1)
df1$type = factor(df1$type)
df1$strand = factor(df1$strand)
p1 <- ggplot(df1,aes(strand,PBC))+geom_boxplot()+facet_grid(.~type)+
  theme(legend.position = "none")
print(p1)
```

- For this plot, the PBC coefficents was calculated using only the reads with certain strand. In particular, we can see that for all 3 types, the boxplots for both strands are very similar.
- The observations of figure 1 hold for both strands.
- Also, we can see that for both ChIP-Seq types, the overall level of the PBC calculated using both strands is lower than the PBC level calculating only one strand (in particular the level of the PBC score is approximately the same for both strands). However, for ChIP-Exo, we can see that the level of the PBC score increases when both strands are joined.
